\section{Examples of Conformal Structures; Analytic Functions}
\subsection{Covering Maps and Analyticity}
\begin{lemma}\label{covering_conformal}
    If $\pi:\tilde{R}\to R$ is a covering map where $R$ is a Riemann surface, then there is a unique conformal structure on $\tilde{R}$ such that $\pi$ is analytic.
\end{lemma}
\begin{proof}
    We construct an atlas on $\tilde{R}$ as follows:
    For $p\in\tilde{R}$, as $\pi$ is a covering map, there is an open neighbourhood $\tilde{N}_p$ of $p$ such that $\pi|_{\tilde{N}_p}:\tilde{N}_p\to N_p$ is a homeomorphism for some neighbourhood $N(p)$ of $\pi(p)$.
    Now there is a conformal structure on $R$, so we can pick a chart $(\phi_p,U_p)$ on $R$ such that $p\in U_p$.
    Our desired chart is then $(\tilde{\phi}_p,\tilde{U}_p)$ where $\tilde{U}_p=(\pi|_{\tilde{N}_p})^{-1}(N_p\cap U_p)$ and $\tilde{\phi}_p=\phi_p|_{N_p\cap U_p}\circ\pi|_{\tilde{U}_p}$.
    It is easy to see it is a chart.
    The collection of all charts produced in this form is an atlas.
    To see this, just observe that the transition function is
    $$\tilde{\phi}_p\circ\tilde{\phi}_q^{-1}=\phi_p\circ\pi\circ\pi^{-1}\circ\phi_q^{-1}=\phi_p\circ\phi_q^{-1}$$
    (with proper restrictions to local open sets) which is analytic as we got $\phi_p,\phi_q$ from another atlas.
    So it extends to a conformal structure $\tilde{A}$ on $\tilde{R}$.\\
    We shall show that $\pi$ is analytic in this choice of conformal structure.
    Let $p\in\tilde{R}$ and choose chart $(\phi_p,U_p)$ in $R$ around $\pi(p)$ and chart $(\tilde{\phi}_p,\tilde{U}_p)$ in $\tilde{R}$ constructed from $(\phi_p,U_p)$ in the above way.
    Then with proper restrictions,
    $$\phi_p\circ\pi\circ\tilde{\phi}_p^{-1}=\phi_p\circ\pi\circ\pi^{-1}\circ\phi_p^{-1}=\operatorname{id}_{\mathbb C}$$
    which is analytic.
    We are then done by Lemma \ref{analytic_local}.\\
    To see the uniqueness of this conformal structure, let $\tilde{B}$ be any conformal structure on $\tilde{R}$ such that $\pi$ is analytic.
    Let $p\in\tilde{R}$, $(\psi,V)\in\tilde{B}$ a chart around $p$ and $(\phi_p,U_p)$ a chart around $f(p)$.
    But then locally the transition function $\tilde\phi_p\circ\psi^{-1}=\phi_p\circ\pi\circ\psi^{-1}$ is analytic.
    So by maximality $\tilde{B}=\tilde{A}$.
\end{proof}
\begin{example}
    Consider the Riemann surface $R$ associated with $\log$ we considered earlier.
    Let $f,\pi$ be the functions as usual.
    As $\pi$ is a covering map, there is a unique way to make $R$ a Riemann surface by the preceding lemma where $\pi:R\to C_\star$ is analytic.
    Furthermore, locally $f|_{U_{I(n)}}=f_{I(n)}\circ\pi$, so $f$ is analytic as well.\\
    Furthermore, we know that there is a homeomorphism $f_{I(n)}:U_{I(n)}\to\tilde{V}_{I(n)}$ (where $\tilde{V}_I=\mathbb R+iI$) having $\exp|_{\tilde{V}_{I(U)}}$ as inverse.
    Then $f_{I(n)}^{-1}$ agree wherever their domains intersect, so we can piece them together to give a conformal equivalence between $R$ and $\mathbb C$.
\end{example}
\begin{example}
    Similar case happened with $R_k$ and $\sqrt[k]{\cdot}$.
    Again $\pi$ induces a unique conformal structure on $R_k$ that makes it and $g$ analytic.
    By the same argument as above, we get $g$ is a conformal equivalence.\\
    Actually, we can even do better with this example.
    Note that the singularities in $0$ and $\infty$ are removable by identifying $\hat{p}_k(0)=\hat{\pi}(0)=\hat{g}(0)=0$ and $\hat{p}_k(\infty)=\hat{\pi}(\infty)=\hat{g}(\infty)=\infty$ (where $\hat{g},\hat{p}_k,\hat{\pi}$ are our notation for $g,p_k,\pi$ with this extended domain and codomain).
    This gives
    \[
        \begin{tikzcd}
            \hat{R}_k=R_k\cup\{0,\infty\}\arrow{r}{\hat{g}}\arrow[swap]{dr}{\hat{\pi}}&\mathbb C_\infty\arrow{d}{\hat{p}_k}\\
            &\mathbb C_\infty
        \end{tikzcd}
    \]
    which is pretty nice except now $\hat{\pi}$ is not a covering map anymore.
\end{example}